---
title: "BABIES teach vs. learn analyses"
author: "Lucy King"
output: html_notebook
---

# Environment
```{r}
# Libraries
library(tidyverse)
library(ggsci)
library(ggpubr)
library(car)
library(lme4)
library(lmerTest)
library(performance)
library(effectsize)
library(parameters)
library(corrr)
set.seed(123456)

cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# Data
data_home <- "~/Box/Mooddata_Coordinating/BABIES/Data/final_scored_data/"

assignment_file <- paste0(
  data_home, 
  "lab_caregiving_behavior/free_play_intervention_assignment.csv"
)

caregiving_file_lf <- paste0(
  data_home, 
  "lab_caregiving_behavior/free_play_lf_10min_20210106.csv"
)

caregiving_file_wf <- paste0(
  data_home, 
  "lab_caregiving_behavior/free_play_wf_10min_20210106.csv"
)

free_play_master_file <- "~/Box/Mooddata_Coordinating/BABIES/Data/final_scored_data/lab_caregiving_behavior/raw_data/PCIRS_FreePlay_MASTER_20200508.xlsx"

demographics_file <- paste0(
  data_home,
  "demographics/demo_6mo_cleaned_final.csv"
)
cesd_file <- paste0(
  data_home,
  "CESD/cesd_6mo_complete.csv"
)
shipley_file <- paste0(
  data_home,
  "shipley/shipley_6mo_final_20200208.csv"
)
crisys_file <- paste0(
  data_home,
  "CRISYS/crisys_scored_6mo_complete.csv"
)

```

# Randomly pick control dyads to match sample size of largest treatment group
Inclusion criteria: infant showed no significant fussiness during last two epochs of free play 
```{r}
all_fp_data <-
  read_csv(caregiving_file_lf) %>% 
  filter(!is.na(intrus_FP)) %>% 
  distinct(ID) # plus 3 never coded

possible_controls <- #
  read_csv(caregiving_file_lf) %>% 
  left_join(read_csv(assignment_file), by = "ID") %>% 
  left_join(read_csv(demographics_file) %>% select(ID, behav_visit_date),  by = "ID") %>% 
  filter(is.na(group)) %>% 
  filter(!ID %in% c(126, 129, 131, 137, 1059, 1062, 1066, 1070, 1077)) # these IDs attempted intervention but were ultimately excluded (infant distress, diaper changing, did not understand instructions)

possible_controls_n <- possible_controls %>% summarise(n_distinct(ID)) %>% pull() # plus 1 never coded

possible_controls %>% 
  filter(episode >= 4, negmood_FP > 2.5) %>% 
  summarise(n_distinct(ID))
```
```{r}
controls <-
  possible_controls %>% 
  filter(episode >= 4) %>% 
  filter(negmood_FP < 3) %>% 
  distinct(ID) %>% 
  sample_n(size = 22) %>% 
  mutate(group = "control")

assignment <-
  read_csv(assignment_file) %>% 
  bind_rows(controls)
```
# Read in data
Videos that can be use in presentations_________________________________________

Learn group:
Decreased by 1: 1057 (can share but not with non-scientific groups), 1063, (can share all), 1069 (can share all), 1111 (can share but not with non-scientific groups)
Decreased by 1.5: 112 (can share all)
Stayed the same: 122 (can share all), 1103 (can share all)

```{r}
d <-
  read_csv(caregiving_file_lf) %>% 
  left_join(assignment, by = "ID") %>% 
  filter(!is.na(group)) %>% 
  left_join(read_csv(demographics_file), by = "ID") %>% 
  left_join(read_csv(cesd_file), by = "ID") %>% 
  left_join(read_csv(shipley_file), by = "ID") %>% 
  left_join(read_csv(crisys_file), by = "ID") %>% 
  mutate(
    male = as.factor(male),
    group = as.factor(group),
    episode_f = as.factor(episode),
    college_or_higher = fct_collapse(
      education_txt,
      below = c(
        "Trade/technical/vocational training",
        "Associate degree",
        "High school graduate/diploma/equivalent (i.e. GED)",
        "Some college credit, no degree"
      ),
      college_or_higher = c(
        "Bachelor's degree",
        "Graduate degree"
      )
    ),
    only_child = as.factor(
      if_else(
        ppl_in_home_allchild > 1,
        "not", "only child"
      )
    ),
    poc = if_else(
      mom_race != "White" | mom_latinx == 1,
      "POC", "White, Non-Hispanic"
    )
  ) 

da <-
  d %>% 
  filter(episode >= 4)

d_wf <-
  read_csv(caregiving_file_wf) %>% 
  left_join(assignment, by = "ID") %>% 
  filter(!is.na(group)) %>% 
  left_join(read_csv(demographics_file), by = "ID") %>% 
  left_join(read_csv(cesd_file), by = "ID") %>% 
  left_join(read_csv(shipley_file), by = "ID") %>% 
  left_join(read_csv(crisys_file), by = "ID") %>% 
  mutate(
    male = as.factor(male),
    group = as.factor(group),
    college_or_higher = fct_collapse(
      education_txt,
      below = c(
        "Trade/technical/vocational training",
        "Associate degree",
        "High school graduate/diploma/equivalent (i.e. GED)",
        "Some college credit, no degree"
      ),
      college_or_higher = c(
        "Bachelor's degree",
        "Graduate degree"
      )
    ),
    only_child = as.factor(
      if_else(
        ppl_in_home_allchild > 1,
        "not", "only child"
      )
    ),
    poc = if_else(
      mom_race != "White" | mom_latinx == 1,
      "POC", "White, Non-Hispanic"
    )
  )

fp_master <-
  readxl::read_xlsx(free_play_master_file) %>% 
  mutate_at(
    vars(Sens_R2:NegMood_R2, Sens_R1:NegMood_R1),
    funs(as.double)
  ) %>% 
  rename_at(
    vars(Sens_R2:NegMood_R2, Sens_R1:NegMood_R1),
    funs(str_to_lower)
  ) 

```

# Cell sizes
```{r}
d %>% 
  distinct(ID, .keep_all = TRUE) %>% 
  count(group)

da %>% 
  filter(group == "learn")
```

# Examine missingness
```{r}
d_wf %>% 
  count(is.na(mom_age))

d_wf %>% 
  count(is.na(ppl_in_home_allchild))

d_wf %>% 
  count(is.na(education))

d_wf %>% 
  count(group, is.na(shipley_6mo_total))

d_wf %>% 
  count(group, is.na(cesd_total))

d_wf %>% 
  count(group, is.na(crisys_total))
```

# Descriptive statistics

## Sample characteristics table
```{r}
d_sample_means <-
  d_wf %>% 
  group_by(group) %>% 
  summarise_at(
    vars(
      age_behav,
      mom_age,
      income_needs,
      cesd_total,
      crisys_total,

    ),
    funs(mean), na.rm = TRUE
  ) %>% 
  gather(variable, mean, -group)

d_sample_sds <-
  d_wf %>% 
  group_by(group) %>% 
  summarise_at(
    vars(
      age_behav,
      mom_age,
      income_needs,
      cesd_total,
      crisys_total
    ),
    funs(sd), na.rm = TRUE
  ) %>% 
  gather(variable, sd, -group)

d_sample_mins <-
  d_wf %>% 
  group_by(group) %>% 
  summarise_at(
    vars(
      age_behav,
      mom_age,
      income_needs,
      cesd_total,
      crisys_total
    ),
    funs(min), na.rm = TRUE
  ) %>% 
  gather(variable, min, -group)

d_sample_maxs <-
  d_wf %>% 
  group_by(group) %>% 
  summarise_at(
    vars(
      age_behav,
      mom_age,
      income_needs,
      cesd_total,
      crisys_total,
    ),
    funs(max), na.rm = TRUE
  ) %>% 
  gather(variable, max, -group)

d_sample_means %>% 
  left_join(d_sample_sds, by = c("group", "variable")) %>% 
  left_join(d_sample_mins, by = c("group", "variable"))  %>% 
  left_join(d_sample_maxs, by = c("group", "variable")) %>% 
  pivot_wider(
    names_from = group,
    values_from = mean:max
  )  %>% 
  mutate_at(
    vars(mean_control:max_teach),
    funs(round(., 2))
  ) %>% 
  mutate(
    mean_control = paste(mean_control, sd_control, sep = ", "),
    mean_teach = paste(mean_teach, sd_teach, sep = ", "),
    mean_learn = paste(mean_learn, sd_learn, sep = ", ")
  )
```

```{r}
d_wf %>% 
  count(group, college_or_higher) %>% 
  pivot_wider(
    names_from = group,
    values_from = n
  )
```

```{r}
d_wf %>% 
  count(group, mom_race) %>% 
  arrange(group, desc(n)) %>% 
  pivot_wider(
    names_from = group,
    values_from = n
  )
```

```{r}
d_wf %>% 
  count(group, mom_latinx) %>% 
  pivot_wider(
    names_from = group,
    values_from = n
  )
```

```{r}
d_wf %>% 
  count(group, male) %>% 
  pivot_wider(
    names_from = group,
    values_from = n
  )
```

```{r}
d_wf %>% 
  count(group, only_child) %>% 
  pivot_wider(
    names_from = group,
    values_from = n
  )
```

## Reliability

### Covariates
```{r}
d_wf %>% 
  dplyr::select(
    cesd_1:cesd_20
  ) %>% 
  psych::alpha()

d_wf %>% 
  dplyr::select(
    crisys_1:crisys_68
  ) %>% 
  psych::alpha()
```

### Caregiving behavior
```{r}
#intrusiveness
fp_master %>%
  filter(Episode < 4) %>% 
  dplyr::select(
    intrus_r1,
    intrus_r2
  ) %>% 
  na.omit() %>% 
  psych::ICC()
```

```{r}
#sensitivity
fp_master %>%
  filter(Episode < 4) %>% 
  dplyr::select(
    sens_r1,
    sens_r2
  ) %>% 
  na.omit() %>% 
  psych::ICC()
```

```{r}
#stimulation
fp_master %>%
  filter(Episode < 4) %>% 
  dplyr::select(
    stim_r1,
    stim_r2
  ) %>% 
  na.omit() %>% 
  psych::ICC()
```
```{r}
#positive regard
fp_master %>%
  filter(Episode < 4) %>% 
  dplyr::select(
    posreg_r1,
    posreg_r2
  ) %>% 
  na.omit() %>% 
  psych::ICC()
```

```{r}
#negative regard
fp_master %>%
  filter(Episode < 4) %>% 
  dplyr::select(
    negreg_r1,
    negreg_r2
  ) %>% 
  na.omit() %>% 
  psych::ICC()
```

```{r}
#detachment
fp_master %>%
  filter(Episode < 4) %>% 
  dplyr::select(
    detach_r1,
    detach_r2
  ) %>% 
  na.omit() %>% 
  psych::ICC()
```
## Distributions of caregiving behaviors
```{r}
da %>% 
  dplyr::select(
    group,
    episode_f,
    Intrusiveness = intrus_FP,
    Sensitivity = sens_FP,
    `Cog. stimulation` = stim_FP,
    `Positive regard` = posreg_FP,
    `Negative regard` = negreg_FP,
    Detachment = detach_FP
  ) %>% 
  mutate(
     episode_f = recode_factor(
      episode_f,
      "4" = "Time 1",
      "5" = "Time 2"
    ),
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  gather(
    key, 
    value,
    Intrusiveness:Detachment
  ) %>% 
  mutate(
    key = factor(
      key,
      levels = c(
        "Intrusiveness",
        "Sensitivity",
        "Cog. stimulation",
        "Positive regard",
        "Negative regard",
        "Detachment"
      )
    )
  ) %>% 
  ggplot(aes(value, fill = group)) +
  geom_density(alpha = 1/2) +
  scale_fill_manual(values = cbbPalette) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    fill = "Group"
  ) +
  facet_grid(key~episode_f, scales = "free")


ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/group_caregiving_density_plots.png",
  dpi = 600,
  width = 7,
  height = 12
)
```

## Examine matching across groups
Variables examined: age, income-to-needs ratio, education, person of color, number of children, depressive symptoms, infant sex

### Distributions for continuous covariates
```{r}
d_wf %>% 
  dplyr::select(
    group,
    `Infant age (months)` = age_behav,
    `Maternal age (years)` = mom_age,
    `Income-to-needs ratio` = income_needs,
    `Maternal depressive symptoms` = cesd_total,
    `Maternal recent life stress` = crisys_total
  ) %>% 
  gather(
    key, 
    value,
    -group
  ) %>% 
  mutate(
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  ggplot(aes(value, fill = group)) +
  geom_density(alpha = 1/2) +
  scale_fill_manual(values = cbbPalette) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    fill = "Group"
  ) +
  facet_wrap(.~key, scales = "free")


ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/group_matching_density_plots.png",
  dpi = 600,
  width = 12,
  height = 7
)
```

### Test differences
```{r}
chisq.test(d_wf$college_or_higher, d_wf$group) 
chisq.test(d_wf$poc, d_wf$group) 
chisq.test(d_wf$male, d_wf$group) 
chisq.test(d_wf$only_child, d_wf$group) 
chisq.test(d_wf$mom_latinx, d_wf$group) 

Anova(lm(mom_age ~ group, data = d_wf), type = 3) # marginal
Anova(lm(income_needs ~ group, data = d_wf), type = 3) 
Anova(lm(cesd_total ~ group, data = d_wf), type = 3) 
Anova(lm(crisys_total ~ group, data = d_wf), type = 3)
Anova(lm(age_behav ~ group, data = d_wf), type = 3)
```

# Test pre-registered hypotheses
We hypothesize that an instruction delivered after epoch 4 regarding the parent’s goal for epoch 5 will result in a change in maternal intrusiveness (relative to a control group with no instruction), such that, compared to epoch 4, a “teach” goal will result in increased intrusiveness during epoch 5 whereas a “learn” goal will result in decreased intrusiveness during epoch 5. We hypothesize no change in intrusiveness from epoch 4 to epoch 5 for the control (no instruction) group. Thus, we hypothesize that time (epoch 4, epoch 5) and group (control, teach, learn) will interact to explain variation in maternal intrusiveness.

## Dummy-code episode and group
```{r}
da <-
  da %>% 
  mutate(
    episode_f = as.factor(episode),
    group = as.factor(group)
  )
```

## Omnibus interaction effect with control group as baseline
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1)
) 
contrasts(da$episode_f) # pre-treatment is baseline

mlm_h_c <-
  lmer(
    intrus_FP ~
      group * episode_f + (1|ID),
    data = da
  )

anova(mlm_h_c)

model_parameters(
  mlm_h_c, 
  standardize = "refit",
  df_method = "satterthwaite"
)

performance(mlm_h_c)
```

## Simple effects

## learn group as baseline
```{r}
contrasts(da$group) = cbind( # learn group is baseline
  "control" = c(1, 0, 0),
  "teach" = c(0, 0, 1)
)

mlm_h_l <-
  lmer(
    intrus_FP ~
      group * episode_f + (1|ID),
    data = da
  )
summary(mlm_h_l)

parameters(
  mlm_h_l, 
  standardize = "refit",
  df_method = "satterthwaite"
)
```

## teach group as baseline
```{r}
contrasts(da$group) = cbind( # teach group is baseline
  "control" = c(1, 0, 0),
  "learn" = c(0, 1, 0)
)

mlm_h_t <-
  lmer(
    scale(intrus_FP) ~
      group * episode_f + (1|ID),
    data = da
  )

summary(mlm_h_t)

parameters(
  mlm_h_t, 
  standardize = "refit",
  df_method = "satterthwaite"
)

```

Supporting our hypothesis, change in intrusiveness depended on group assignment. For the control group, there was no change in intrusiveness. For the learn group, there was a non-significant decrease in intrusiveness. For the teach group, there was a significant increase in intrusiveness.

## Visualize zero-order effects 
```{r}
da_summary <-
  da %>% 
  mutate(
    episode_f = recode_factor(
      episode_f,
      "4" = "Time 1",
      "5" = "Time 2"
    )
  ) %>% 
  group_by(group, episode_f) %>% 
  summarise(
    n = n(),
    Intrusiveness = mean(intrus_FP),
    intrus_sd = sd(intrus_FP),
    intrus_se = intrus_sd / sqrt(n),
    cog_stim = mean(stim_FP, na.rm = TRUE),
    cog_stim_sd = sd(stim_FP, na.rm = TRUE),
    cog_stim_se = cog_stim_sd / sqrt(n),
    posreg = mean(posreg_FP),
    posreg_sd = sd(posreg_FP),
    posreg_se = posreg_sd / sqrt(n)
  )
```

```{r}
da %>% 
  mutate(
    episode_f = recode_factor(
      episode_f,
      "4" = "Baseline",
      "5" = "Post-intervention"
    )
  ) %>% 
  ggplot(aes(episode_f, intrus_FP, fill = group)) +
  geom_boxplot() +
  scale_fill_manual(values = cbbPalette) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    y = "Maternal intrusiveness",
    fill = "Intervention group"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/hypothesis_boxplot.png",
  dpi = 600,
  width = 7,
  height = 5
)

```

```{r}
gg_summary_p <- 
  da_summary %>% 
  mutate(
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  ggplot(aes(episode_f, Intrusiveness, color = group)) 


gg_summary_p +
  geom_pointrange(
    aes(ymin = Intrusiveness - intrus_se, ymax = Intrusiveness + intrus_se),
    size = 1.25
  ) +
  geom_line(aes(group = group), size = 2) +
  scale_colour_manual(values=cbbPalette) +
  scale_y_continuous(breaks = seq.int(1, 7, .5), limits = c(1, 4)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    y = "Maternal intrusiveness",
    color = NULL
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/hypothesis_lineplot.png",
  dpi = 600,
  width = 6,
  height = 5
)
```

## N (%) increased, descreased, etc. 
```{r}
intrus_diff <-
  da %>% 
  select(ID, group, episode, intrus_FP) %>% 
  pivot_wider(
    names_from = episode,
    values_from = intrus_FP
  ) %>% 
  mutate(
    intrus_diff = `5` - `4`, 
    increased = intrus_diff > 0, 
    decreased = intrus_diff < 0,
    stable = intrus_diff == 0
  ) 

intrus_diff %>% 
  count(group, increased) %>% 
  group_by(group) %>% 
  mutate(per = n / sum(n))

intrus_diff %>% 
  filter(group == "learn", decreased == TRUE)
```

# Additional analyses

## Covarying for infant sex and only child

```{r}
da <-
  da %>% 
  mutate(
    male = as.factor(male)
  )
```

```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1)
) 
contrasts(da$male) = c(-.5, .5) # effect code sex

mlm_h_c_planned_wf <-
  lmer(
    intrus_FP ~
      group * episode_f + (1|ID) +
      only_child +
      male,
    data = da
  )

anova(mlm_h_c_planned_wf)
parameters(mlm_h_c_planned_wf, standardize = "refit")
```

## Using all free play data

```{r}
d <-
  d %>% 
  mutate(
    group = as.factor(group),
    male = as.factor(male),
    episode_pc = as.factor(
      case_when(
        episode == 1 ~ 0,
        episode == 2 ~ 0,
        episode == 3 ~ 0,
        episode == 4 ~ 0,
        episode == 5 ~ 1
      )
    )
  )
```

## Omnibus interaction effect with control group as baseline
```{r}
contrasts(d$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1)
) 
contrasts(d$episode_pc)

mlm_h_c_all <-
  lmer(
    intrus_FP ~
      group * episode_pc + (1|ID),
    data = d
  )
anova(mlm_h_c_all)
parameters(mlm_h_c_all)
performance(mlm_h_c_all)
```
## learn group as baseline
```{r}
contrasts(d$group) = cbind( # learn group is baseline
  "control" = c(1, 0, 0),
  "teach" = c(0, 0, 1)
)

mlm_h_l_all <-
  lmer(
    intrus_FP ~
      group * episode_pc + (1|ID),
    data = d
  )
summary(mlm_h_l_all)
parameters(mlm_h_l_all)
```

## teach group as baseline
```{r}
contrasts(d$group) = cbind( # teach group is baseline
  "control" = c(1, 0, 0),
  "learn" = c(0, 1, 0)
)

mlm_h_t_all <-
  lmer(
    intrus_FP ~
      group * episode_pc + (1|ID),
    data = d
  )
parameters(mlm_h_t_all)
```

## Other caregiving behaviors

### Correlations
```{r}
da_time_1 <-
  da %>% 
  filter(episode == "4")

da_time_2 <-
  da %>% 
  filter(episode == "5")

da_time_1 %>% 
  select(stim_FP, education, income_needs) %>% 
  correlate() %>% 
  shave(upper = FALSE) %>% 
  fashion() 

da_time_2 %>% 
  select(stim_FP, education, income_needs) %>% 
  correlate() %>% 
  shave(upper = FALSE) %>% 
  fashion()
```

### Sensitivity
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)
contrasts(da$episode_f) # pre-treatment is baseline

mlm_sens_c <-
  lmer(
    sens_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_sens_c)
parameters(mlm_sens_c)
```

### Warmth
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_posreg_c <-
  lmer(
    posreg_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_posreg_c)
parameters(mlm_posreg_c, standardize = "refit")
performance(mlm_posreg_c)
```

```{r}
contrasts(da$group) = cbind( # learn group is baseline
  "control" = c(1, 0, 0),
  "teach" = c(0, 0, 1) 
)

mlm_posreg_l <-
  lmer(
    posreg_FP ~
      group * episode + (1|ID),
    data = da
  )

parameters(mlm_posreg_l, standardize = "refit")
```

```{r}
contrasts(da$group) = cbind( # teach group is baseline
  "control" = c(1, 0, 0),
  "learn" = c(0, 1, 0) 
)

mlm_posreg_t <-
  lmer(
    posreg_FP ~
      group * episode + (1|ID),
    data = da
  )

parameters(mlm_posreg_t, standardize = "refit")
```

#### Visualize
```{r}
gg_summary_p_posreg <- 
  da_summary %>% 
  mutate(
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  ggplot(aes(episode_f, posreg, color = group)) 


gg_summary_p_posreg +
  geom_pointrange(
    aes(ymin = posreg - posreg_se, ymax = posreg + posreg_se),
    size = .75
  ) +
  geom_line(aes(group = group), size = 2) +
  scale_colour_manual(values=cbbPalette) +
  scale_y_continuous(breaks = seq.int(1, 7, .5), limits = c(1, 6)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    y = "Maternal positive regard/warmth",
    color = NULL
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/lineplot_posreg.png",
  dpi = 600,
  width = 6,
  height = 5
)
```


### Cognitive stimulation
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_stim_c <-
  lmer(
    stim_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_stim_c)
parameters(mlm_stim_c, standardize = "refit")
performance(mlm_stim_c)
```

```{r}
contrasts(da$group) = cbind( # learn group is baseline
  "control" = c(1, 0, 0),
  "teach" = c(0, 0, 1) 
)

mlm_stim_l <-
  lmer(
    stim_FP ~
      group * episode + (1|ID),
    data = da
  )

parameters(mlm_stim_l, standardize = "refit")
```

```{r}
contrasts(da$group) = cbind( # teach group is baseline
  "control" = c(1, 0, 0),
  "learn" = c(0, 1, 0) 
)

mlm_stim_t <-
  lmer(
    stim_FP ~
      group * episode + (1|ID),
    data = da
  )

parameters(mlm_stim_t)
```

#### Visualize
```{r}
gg_summary_p_stim <- 
  da_summary %>% 
  mutate(
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  ggplot(aes(episode_f, cog_stim, color = group)) 


gg_summary_p_stim +
  geom_pointrange(
    aes(ymin = cog_stim - cog_stim_se, ymax = cog_stim + cog_stim_se),
    size = .75
  ) +
  geom_line(aes(group = group), size = 2) +
  scale_colour_manual(values=cbbPalette) +
  scale_y_continuous(breaks = seq.int(1, 7, .5), limits = c(1, 5)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    y = "Maternal cognitive stimulation",
    color = NULL
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/lineplot_stim.png",
  dpi = 600,
  width = 6,
  height = 5
)
```


### Negative Regard
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_negreg_c <-
  lmer(
    negreg_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_negreg_c)
```

### Detachment
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_detach_c <-
  lmer(
    detach_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_detach_c)
```
### Infant negative mood
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_negmood_c <-
  lmer(
    negmood_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_negmood_c)
```

### Infant positive mood
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_posmood_c <-
  lmer(
    posmood_FP ~
      group * episode + (1|ID),
    data = da
  )

anova(mlm_posmood_c)
```

### Covarying for cognitive stimulation and warmth
```{r}
da <-
  da %>% 
  group_by(ID) %>% 
  mutate(
    stim_FP_mean = mean(stim_FP, na.rm = TRUE), 
    stim_FP_pc = stim_FP - stim_FP_mean,
    posreg_FP_mean = mean(posreg_FP), 
    posreg_FP_pc = posreg_FP - posreg_FP_mean,
    intrus_FP_mean = mean (intrus_FP, na.rm = TRUE),
    intrus_FP_pc = intrus_FP - intrus_FP_mean
  ) %>% 
  ungroup()
```

#### Cognitive stimulation
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_h_c_stim <-
  lmer(
    intrus_FP ~
      group * episode_f + 
      stim_FP_mean +
      stim_FP_pc +
      (1|ID),
    data = da
  )
anova(mlm_h_c_stim)
parameters(mlm_h_c_stim, standardize = "refit")
performance(mlm_h_c_stim)
```
```{r}
contrasts(da$group) = cbind( # learn group is baseline
  "control" = c(1, 0, 0),
  "teach" = c(0, 0, 1) 
)

mlm_h_l_stim <-
  lmer(
    intrus_FP ~
      group * episode_f + 
      stim_FP_mean +
      stim_FP_pc +
      (1|ID),
    data = da
  )
parameters(mlm_h_l_stim, standardize = "refit")
```

##### Visualize

```{r}
da %>% 
  mutate(
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  ggplot(aes(stim_FP_pc, intrus_FP, color = group)) +
  geom_jitter(size = 3, alpha = 1/3, color = "black") +
  geom_smooth(method = "lm", size = 2, se = FALSE) +
  scale_y_continuous(breaks = seq.int(1, 7, .5), limits = c(1, 6)) +
  scale_x_continuous(breaks = seq.int(-2, 2, .5)) +
  scale_colour_manual(values=cbbPalette) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = "Cognitive stimulation\n(person-mean-centered)",
    y = "Maternal intrusiveness",
    color = NULL
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/stim_intrus.png",
  dpi = 600,
  width = 6,
  height = 5
)
```

```{r}
contrasts(da$group) = cbind( # reach group is baseline
  "control" = c(1, 0, 0),
  "learn" = c(0, 1, 0) 
)

mlm_h_t_stim <-
  lmer(
    intrus_FP ~
      group * episode + 
      stim_FP_mean +
      stim_FP_pc +
      (1|ID),
    data = da
  )
parameters(mlm_h_t_stim, standardize = "refit")
```

##### In teach group only
```{r}
da_teach <-
  da %>% 
  filter(group == "teach")

mlm_h_stim_teach <-
  lmer(
    intrus_FP ~
      episode_f + 
      stim_FP_mean +
      stim_FP_pc +
      (1|ID),
    data = da
  )
anova(mlm_h_stim_teach)
parameters(mlm_h_stim_teach, standardize = "refit")
performance(mlm_h_stim_teach)
```

#### Warmth
```{r}
contrasts(da$group) = cbind( # control group is baseline
  "learn" = c(0, 1, 0),
  "teach" = c(0, 0, 1) 
)

mlm_h_c_posreg <-
  lmer(
    intrus_FP ~
      group * episode_f + 
      posreg_FP_mean +
      posreg_FP_pc +
      (1|ID),
    data = da
  )
anova(mlm_h_c_posreg)
parameters(mlm_h_c_posreg, standardize = "refit")
performance(mlm_h_c_posreg)
```

```{r}
contrasts(da$group) = cbind( # learn group is baseline
  "control" = c(1, 0, 0),
  "teach" = c(0, 0, 1) 
)

mlm_h_l_posreg <-
  lmer(
    intrus_FP ~
      group * episode + 
      posreg_FP_mean +
      posreg_FP_pc +
      (1|ID),
    data = da
  )
parameters(mlm_h_l_posreg, standardize = "refit")
```

```{r}
contrasts(da$group) = cbind( # reach group is baseline
  "control" = c(1, 0, 0),
  "learn" = c(0, 1, 0) 
)

mlm_h_t_posreg <-
  lmer(
    intrus_FP ~
      group * episode + 
      posreg_FP_mean +
      posreg_FP_pc +
      (1|ID),
    data = da
  )
parameters(mlm_h_t_posreg, standardize = "refit")
```

#### Visualize

```{r}
da %>% 
  mutate(
    group = recode_factor(
      group,
      "control" = "Control",
      "teach" = "Teach",
      "learn" = "Learn"
    )
  ) %>% 
  ggplot(aes(posreg_FP_pc, intrus_FP, color = group)) +
  geom_jitter(size = 3, psych::alpha = 1/3, color = "black") +
  geom_smooth(method = "lm", size = 2, se = FALSE) +
  scale_y_continuous(breaks = seq.int(1, 7, .5), limits = c(1, 6)) +
  scale_x_continuous(breaks = seq.int(-2, 2, .5)) +
  scale_colour_manual(values=cbbPalette) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  ) +
  labs(
    x = "Positve regard\n(person-mean-centered)",
    y = "Maternal intrusiveness",
    color = NULL
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/teach_learn/figures/posreg_intrus.png",
  dpi = 600,
  width = 6,
  height = 5
)
```


  